\documentclass[a4paper,11pt]{article}

\usepackage[left=0.6in, right=0.6in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=10pt}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{url}
\urlstyle{same}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black
}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.1}

\usepackage{titlesec}
\titlespacing*{\section}{0pt}{10pt}{6pt}
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\begin{document}
\small

%==========================
% HEADER
%==========================
\begin{center}
    {\huge \textbf{DEEPAK MODI}}\\[6pt]
    New Delhi, IN \textbar\ +91 8676842176 \textbar\
    \href{mailto:deepakmodi8676@gmail.com}{\nolinkurl{deepakmodi8676@gmail.com}} \textbar\
    \href{https://deepakmodi.dev}{\texttt{deepakmodi.dev}}
\end{center}

%==========================
% SUMMARY
%==========================
\section*{SUMMARY}
Full-Stack Developer and final-year B.Tech CSE student with expertise in AI web integrations. Proven track record building scalable applications serving 1000+ users with experience in React, Next.js, TypeScript, and modern web technologies.

%==========================
% TECHNICAL SKILLS
%==========================
\section*{TECHNICAL SKILLS}
\textbf{Programming Languages:} JavaScript (ES6+), TypeScript, Java, Python, C++\\
\textbf{Frontend Web Development:} HTML5, CSS3, React.js, Next.js, Vue.js, Nuxt.js, Tailwind CSS\\
\textbf{Backend \& Databases:} Node.js, Express.js, REST APIs, GraphQL, MongoDB, PostgreSQL, Firebase, Supabase\\
\textbf{Tools \& Platforms:} Git, GitHub, VS Code, NPM, Postman, Livekit, Vercel, Netlify\\
\textbf{Generative AI \& Automation:} LLMs, NLP, RAG, LangChain, n8n, Vector Databases, AI Agents, Gemini API\\
\textbf{Other Skills:} System Design (basics), CI/CD (GitHub Actions), Unit Testing, AWS (basics)

%==========================
% EXPERIENCE
%==========================
\section*{EXPERIENCE}

\textbf{Full Stack Developer Intern} \hfill \textit{Dec 2025 -- Present}\\
\textit{TidyHire (Param AI), Hyderabad (Remote)} \hfill \href{https://tidyhire.app}{\texttt{tidyhire.app}}
\begin{itemize}
    \item Developed key modules for Charlie (AI Interviewer) and Ria (Outbound Call Agent) using Node.js \& Express.js.
    \item Built high-performance responsive layouts for the recruitment dashboard using Nuxt.js and Tailwind CSS.
    \item Integrated real-time features for the AI recruitment system, enhancing user interaction and data visualization.
\end{itemize}

\vspace{2pt}

\textbf{Frontend Developer Intern} \hfill \textit{Sept 2025 -- Nov 2025}\\
\textit{Cekura AI (YC F24), San Francisco, CA (Remote)} \hfill \href{https://www.cekura.ai}{\texttt{cekura.ai}}
\begin{itemize}
    \item Contributed to a YC-backed startup building the reliability layer for conversational AI agents used across enterprise teams.
    \item Developed intuitive dashboards for automated testing, monitoring, and observability of voice and chat AI systems.
    \item Built interactive front-end layouts using TypeScript, Next.js, Tailwind CSS, and shadcn UI.
\end{itemize}

\vspace{2pt}

\textbf{Software Development Intern} \hfill \textit{July 2025 -- Sept 2025}\\
\textit{Nile Wellness \& Medicare Pvt Ltd, Gurugram (Remote)} \hfill \href{https://www.nilewellness.com}{\texttt{nilewellness.com}}
\begin{itemize}
    \item Developed multi-tenant treatment and lead-generation pages for five major Indian hospitals serving international patients.
    \item Converted 50+ Figma designs into responsive, high-performance React components aligned with brand requirements.
    \item Integrated OneSignal notifications, Google Ads tracking, and multi-language support using Next.js and Radix UI.
\end{itemize}

%==========================
% PROJECTS
%==========================
\section*{PROJECTS}

\textbf{ResumeGPT} \hfill \href{https://tryresumegpt.vercel.app}{\texttt{tryresumegpt.vercel.app}}
\begin{itemize}
    \item Built an AI-powered resume generator converting natural language prompts into professional, ATS-friendly resumes.
    \item Scaled to 200+ active users with integrated ATS scoring, RAG content suggestions, and optimization features.
    \item Developed using Next.js, TypeScript, Prisma ORM, NextAuth, and Gemini API for authentication and AI capabilities.
\end{itemize}

\vspace{2pt}

\textbf{MenuViz} \hfill \href{https://menuviz.vercel.app}{\texttt{menuviz.vercel.app}}
\begin{itemize}
    \item Built an AI-powered creative studio for restaurants to generate food images, menus, posters, logos, and branding assets.
    \item Implemented AI prompt enhancement, image gallery with filtering, generation history, user settings, and data persistence.
    \item Developed with Next.js 16, TypeScript, Tailwind CSS 4, shadcn/ui, Supabase, Gemini-3-Pro API and Vercel AI SDK.
\end{itemize}

\vspace{2pt}

\textbf{NotesNeo} \hfill \href{https://notesneo.vercel.app}{\texttt{notesneo.vercel.app}}
\begin{itemize}
    \item Built an online study notes platform used by 1000+ university students for semester-wise quality notes access.
    \item Engineered personalized dashboards, favorites, localStorage persistence, PWA support, and mobile-first responsive UI.
    \item Implemented using Next.js 16, TypeScript, Tailwind CSS 4, Radix UI, and live AI chatbot for student support.
\end{itemize}

\vspace{2pt}

\textbf{NeoCompiler} \hfill \href{https://neocompiler.vercel.app}{\texttt{neocompiler.vercel.app}}
\begin{itemize}
    \item Developed a real-time multi-language code editor supporting 10+ languages with collaborative social coding features.
    \item Integrated Monaco Editor, Piston API for execution, and Gemini API for AI-powered coding assistance.
    \item Added public snippets, user profiles, theming, and community feed using React, Firebase Auth, and Tailwind CSS.
\end{itemize}

%==========================
% EDUCATION
%==========================
\section*{EDUCATION}

\textbf{Maharishi Dayanand University, Rohtak} \hfill \textit{2022 -- 2026}\\
Bachelor of Technology, Computer Science Engineering \hfill \textbf{Percentage:} 80\%

\end{document}